\begin{thebibliography}{}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{southam1961} Southam CM, Brunschwig A, 
``Quantitative studies of autotransplantation of human cancer. preliminary report'', 
Cancer 14: 971–978, 1961 

\bibitem{reya2001} Reya T, Morrison SJ, Clarke MF, Weissman IL, 
``Stem cells, cancer, and cancer stem cells'', 
nature 414: 105–111, 2001 

\bibitem{dick2003} Dick JE,  
``Breast cancer stem cells revealed'', 
Proceedings of the National Academy of Sciences 100: 3547–3549, 2003

\bibitem{schatton2008} Schatton T, Murphy GF, Frank NY, Yamaura K, Waaga-Gasser AM, et al, 
``Identification of cells initiating human melanomas'', 
Nature 451: 345–349, 2008


\bibitem{MathematicalModelingOfLeukemogenesisAndCancerStemCellDynamics} T. Stiehl and A. Marciniak-Czochra,
``Mathematical Modeling of Leukemogenesis and Cancer Stem Cell Dynamic'', 
Math. Model. Nat. Phenom. Vol. 7, No. 1, 2012, pp. 166-202 DOI: 10.1051/mmnp/20127199, 2012

\bibitem{StemCellsAndTheirNiches} KA. Moore, IR. Lemischka, 
``Stem cells and their niches'', 
Science, 311, No. 5769,1880-1805, 2006

\bibitem{TheoryOfSelfReproducingAutomata} Von Neumann, J. and A. W. Burks, 
``Theory of self-reproducing automata'',  
Urbana, University of Illinois Press, 1966

\bibitem{EmergentBehaviors} Jiao Y, Torquato S, 
``Emergent Behaviors from a Cellular Automaton Model for Invasive Tumor Growth in Heterogeneous Microenvironments'', 
PLoS Comput Biol 712: e1002314, 2011 

\bibitem{MicroenvironmentalVariables} Scott JG, Hjelmeland AB, Chinnaiyan P, Anderson ARA, Basanta D, 
``Microenvironmental Variables Must Influence Intrinsic Phenotypic Parameters of Cancer Stem Cells to Affect Tumourigenicity'', 
PLoS Comput Biol 101: e1003433,  2014 


\bibitem{al2003} Al-Hajj M, Wicha MS, Benito-Hernandez A, Morrison SJ, Clarke MF, 
``Prospective identification of tumorigenic breast cancer cells'', 
Proceedings of the National Academy of Sciences 100: 3983–3988, 2003

\bibitem{al2004} Al-Hajj M, Becker MW, Wicha M, Weissman I, Clarke MF,  
``Therapeutic implications of cancer stem cells'', 
Current opinion in genetics \& development 14:43–47, 2004

\bibitem{singh2004} Singh SK, Clarke ID, Hide T, Dirks PB, 
``Cancer stem cells in nervous system tumors'', 
Oncogene 23: 7267–7273,  2004

\bibitem{singh2003} Singh SK, Clarke ID, Terasaki M, Bonn VE, Hawkins C, et al, 
``Identification of a cancer stem cell in human brain tumors'', 
Cancer research 63:5821–5828,  2003 

\bibitem{kondo2004} Kondo T, Setoguchi T, Taga T, 
``Persistence of a small subpopulation of cancer stem-like cells in the c6 glioma cell line'', 
Proceedings of the National Academy of Sciences of the United States of America 101: 781–786, 2004

\bibitem{setoguchi2004} Setoguchi T, Taga T, Kondo T, 
``Cancer stem cells persist in many cancer cell lines'', 
Cell cycle 3: 412–413, 2004

\bibitem{dean2005} Dean M, Fojo T, Bates S, 
``Tumour stem cells and drug resistance'',  
Nature Reviews Cancer 5: 275–284, 2005 

\bibitem{donnenberg2005} Donnenberg VS, Donnenberg AD, 
``Multiple drug resistance in cancer revisited: the cancer stem cell hypothesis'', 
The Journal of Clinical Pharmacology 45: 872–877, 2005

\bibitem{Scott2014} Scott JG, Hjelmeland AB, Chinnaiyan P, Anderson ARa, Basanta D, 
``Microenvironmental variables must influence intrinsic phenotypic parameters of cancer stem cells to affect tumourigenicity'', 
PLoS computational biology 10:e1003433, 2014 

\bibitem{poleszczuk2015} Poleszczuk J, Hahnfeldt P, Enderling H, Rzhetsky A, 
``Evolution and phenotypic selection of cancer stem cells'', 
PLoS computational biology 11:e1004025–e1004025, 2015

\bibitem{morrison2006} Morrison SJ, Kimble J, 
``Asymmetric and symmetric stem-cell divisions in development and cancer'', 
Nature 441: 1068–1074, 2006

\bibitem{caussinus2005} Caussinus E, Gonzalez C, 
``Induction of tumor growth by altered stem-cell asymmetric division in drosophila melanogaster'', 
Nature genetics 37: 1125–1129, 2005

\bibitem{hanahan2000} Hanahan D, Weinberg RA, 
``The hallmarks of cancer'', 
cell 100: 57–70, 2000 

\bibitem{hanahan2011} Hanahan D, Weinberg RA, 
``Hallmarks of cancer: the next generation'', 
cell 144: 646–674, 2011

\bibitem{levental2009} Levental KR, Yu H, Kass L, Lakins JN, Egeblad M, et al. 
``Matrix crosslinking forces tumor progression by enhancing integrin signaling'', 
Cell 139:891–906, 2009 

\bibitem{lu2012} Lu P, Weaver VM, Werb Z, 
``The extracellular matrix: a dynamic niche in cancer progression'', 
The Journal of cell biology 196: 395–406, 2012 

\bibitem{Sottoriva2010} Sottoriva A, Verhoeff JJC, Borovski T, McWeeney SK, Naumov L, et al, 
``Cancer stem cell tumor model reveals invasive morphology and increased phenotypical heterogeneity'', 
Cancer research 70: 46–56,  2010

\bibitem{friedl2003} Friedl P, Wolf K, 
''Tumour-cell invasion and migration: diversity and escape mechanisms'', 
Nature Reviews Cancer 3: 362–374, 2003

\bibitem{wolf2007} Wolf K, Wu YI, Liu Y, Geiger J, Tam E, et al, 
``Multi-step pericellular proteolysis controls the transition from individual to collective cancer cell invasion'', 
Nature cell biology 9: 893–904, 2007

\bibitem{friedl2009} Friedl P, Gilmour D, 
``Collective cell migration in morphogenesis, regeneration and cancer'', 
Nature reviews Molecular cell biology 10: 445–457, 2009 

\bibitem{enderling2008} Enderling H, Alexander NR, Clark ES, Branch KM, Estrada L, et al,  
``Dependence of invadopodia function on collagen fiber spacing and cross-linking:computational modelling and experimental evidence'', 
Biophysical journal 95:2203–2218, 2008

\bibitem{klein2009} Klein EA, Yin L, Kothapalli D, Castagnino P, Byfield FJ, et al, 
``Cell-cycle control by physiological matrix elasticity and in vivo tissue stiffening'', 
Current Biology 19: 1511–1518, 2009

\bibitem{ulrich2009} Ulrich TA, de Juan Pardo EM, Kumar S, 
``The mechanical rigidity of the extracellular matrix regulates the structure, motility, and proliferation of glioma cells'', 
Cancer research 69: 4167–4174, 2009

\bibitem{alexander2008} Alexander NR, Branch KM, Parekh A, Clark ES, Iwueke IC, et al, 
``Extracellular matrix rigidity promotes invadopodia activity'', 
Current Biology 18:1295–1299, 2008

\bibitem{das2013} Das A, Kapoor A, Mehta GD, Ghosh SK, Sen S,  
``Extracellular matrix density regulates extracellular proteolysis via modulation of cellular contractility'', 
J Carcinogene Mutagene S 13, 2013

\bibitem{schneider2012} Schneider CA, Rasband WS, Eliceiri KW, 
``Nih image to imagej: 25 years of image analysis'', 
Nature methods 9: 671–675, 2012

\bibitem{ricci2007} Ricci-Vitiani L, Lombardi DG, Pilozzi E, Biffoni M, Todaro M, et al, 
``Identification and expansion of human colon-cancer-initiating cells'', 
Nature 445:111–115, 2007

\bibitem{Friedl2010} Friedl P, Wolf K, 
``Plasticity of cell migration: a multiscale tuning model'', 
The Journal of cell biology 188: 11–9, 2010 

\bibitem{Wolf2009} Wolf K, Friedl P, 
``Mapping proteolytic cancer cell-extracellular matrix interfaces'', 
Clinical \& experimental metastasis 26: 289–98, 2009

\bibitem{Zaman2006} Zaman MH, Trapani LM, Sieminski AL, Mackellar D, Gong H, et al, 
``Migration of tumor cells in 3D matrices is governed by matrix stiffness along with cell-matrix adhesion and proteolysis'', 
Proceedings of the National Academy of Sciences of the United States of America 103: 10889–10894, 2006

\bibitem{carey2012} Carey SP, Kraning-Rush CM, Williams RM, Reinhart-King CA, 
``Biophysical control of invasive tumor cell behavior by extracellular matrix microarchitecture'', 
Biomaterials 33: 4157–4165, 2012

\bibitem{MechanismOfEnzymaticAndNonenzymaticProlylCisTransIsomerization} Stein RL, 
``Mechanism of Enzymatic and Nonenzymatic Prolyl cis-trans Isomerization'', 
Adv. Protein Chem., 44, 1–24. 1993

\bibitem{ProlylIsomerasesRoleInProteinFolding} Schmid FX, Mayr LM, Mücke M and Schönbrunner ER, 
``Prolyl Isomerases: Role in Protein Folding'', 
Adv. Protein Chem., 44, 25–66. 1993

\bibitem{PeptidylProlylCisTransIsomerasesAndTheirEffectors} Fischer G, 
``Peptidyl-Prolyl cis/trans Isomerases and Their Effectors'', 
Angew. Chem. Int. Ed. Engl., 33, 1415–1436. 1993

\bibitem{IntroductionToAutomataTheory} Hopcroft, John E.; Motwani, Rajeev; Ullman, Jeffrey D, 
``Introduction to Automata Theory, Languages, and Computation'', 
2 ed.. Addison Wesley. ISBN 0-201-44124-1. Retrieved 19 November 2012

\bibitem{lodish2000} Lodish H, Berk A, Zipursky SL, Matsudaira P, Baltimore D, et al, 
``Molecular Cell Biology'', 
4th ed, Section–22.3. WH Freeman, 2000

\bibitem{FiniteStateMachine} Black, Paul E, 
``Finite State Machine. Dictionary of Algorithms and Data Structures'', 
U.S. National Institute of Standards and Technology, 12 May 2008

\bibitem{FirstDraftOfAReportOnTheEDVAC} von Neumann, John, 
``First Draft of a Report on the EDVAC'', 
archived from the original on March 14, 2013, retrieved August 24, 2011, 1945

\bibitem{MolecularBiologyOfTheCell} Alberts B, Johnson A, Lewis J, et al, 
``Molecular Biology of the Cell'', 
4th edition. New York: Garland Science, 2002

\bibitem{cppByDissection} Ira Pohl, University of California, Santa Cruz, 
``C++ By Dissection'', Addison-Wesley,   18 Oct 2001

\bibitem{CellularAutomatonModelingOfBiologicalPatternFormation} Philip Maini, Andreas Deutsch, Sabine Dormann, Germany,
``Cellular Automaton Modeling of Biological Pattern Formation Characterization, Applications, and Analysis'',  
Birkhauser, 2005

\bibitem{SystemsAnalysisandDesign} Lonnie D. Bentley, 
``Systems Analysis and Design for the Global Enterprise'', 
 p.160 7th edition

\bibitem{CambridgeDictionaryOfScienceAndTechnology} Walker, CBE, FRSE, Peter M. B.,
``Cambridge Dictionary of Science and Technology'' reprint ed., 
Edinburgh: Press Syndicate of the University of Cambridge. p. 658. ISBN 0521394414, ed. 1990

\bibitem{TheNatureOfTheChemicalBond} Pauling L, 
``The Nature of the Chemical Bond'', 3rd. ed, 
Cornell University Press. ISBN 0-8014-0333-2, 1960 

\bibitem{SoftwareEngineering} Ian Sommerville, 
``Software engineering'', 9th ed, ISBN-13: 978-0-13-703515-1, ISBN-10: 0-13-703515-2, 2011

\end{thebibliography}

